Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Better case distinction in lem:1req

\begin{proof}
  If no partition of \TAlg's components exist, then it performs no repartition and the cost is $0$.
  Hence, in the following we bound the cost of moving to component-respecting partition.

@@

    Consider a request $(u, v)$ and let $U, V$ be clusters of these nodes.
    If $U=V$, then the request does not require a reconfiguration and \TAlg{} incurs no cost.
    Otherwise, we consider cases upon the type of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is $C_3$ as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

    Finally, we consider the case where both $U$ and $V$ are $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg{} has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    If either $u$ or $v$ belongs to a component of size $2$, then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise no component-respecting partition exists. In this case \TAlg{} exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}

>>>>

\begin{proof}
  If no partition of \TAlg's components exist, then it performs no repartition and the cost is $0$.
  Hence, in the following we bound the cost of moving to a component-respecting partition.

@@

    Consider a request $(u, v)$ that triggered the repartitiong and let $U, V$ be clusters of these nodes.
    Note that $U\neq V$, as such a request cannot trigger a reconfiguration.
    We consider cases upon the type of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is of type $C_3$, as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

    Finally, we consider the case where both $U$ and $V$ are of type $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    If either $u$ or $v$ belongs to a component of size $2$, then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise no component-respecting partition exists. In this case \TAlg exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}
